---
title: "R_Markdown_Presentation_and_Plotly"
author: "Joao Felizardo"
date: "5/21/2019"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown Presentation & Plotly

I'm going to use [The Economic Freedom Index](https://www.kaggle.com/lewisduncan93/the-economic-freedom-index) dataset to show a graphic relating the `Government.Integrity`, `Judical.Effectiveness` and `Financial.Freedom`. For this I'll use the plotly library.

## Setting environment and Getting data
```{r echo=TRUE, warning=FALSE, message=FALSE}
library(plotly)
ef <- read.csv("economic_freedom_index2019_data.csv")
```

## Build graphic

```{r echo=TRUE, warning=FALSE, message=FALSE}
plot_ly(x = ~ef$Government.Integrity, y = ~ef$Judical.Effectiveness, z = ~ef$Financial.Freedom, type = "scatter3d", color = ~ef$Financial.Freedom)
```

## Slide with Plot
As we can see there's a positive correlation between `Government.Integrity`, `Judical.Effectiveness` and `Financial.Freedom`.

